PhD Title \\ PhD Thesis

### 2024-07-24 Latex_files/Thesis/chapters/chapter 3/main.tex
updates

It should be noted that the galvano-mirror requires the use 
of a Keplerian beam expansion arrangement which reduces
the transmitted laser power due to localised heating of the air.
Afterwards the laser is passed through a dichroic mirror that 
separates incoming infrared and visible light, this is to 
prevent the laser from damaging the CCD camera used for imaging
the trapping plane. The laser is then focused to a diffraction
limited spot by a 1.25 NA objective. By increasing the numerical
aperture of the objective, the gradient force at the focal point 
is increased; the trade-off being that the for higher NA values 
the trapping depth is reduced due to spherical aberrations.
While it is possible to increase the trapping depth \cite{Reihani2006} 
by adjusting the objective's tube length this approach is incompatible 
with our trapping arrangement. A 0.25 NA condenser objective refocuses
the scattered laser light and also provide an aperture for an 
imaging LED to illuminate the focal plane. Samples are loaded 
onto a piezo driven table to that is inserted between the trapping
and condensing objectives; the piezo drivers allow for sub-micron
control of the sample position to a degree as small as a 10 nm. 
To detect and monitor the position of a trapped particle a 
quadrant photo diode (QPD) was utilised.

\begin{figure}
	\label{fig:setup}
	\centering
	\includegraphics[height=\linewidth, angle=270]{tweezer_setup.pdf}
	\caption{Optical tweezer set up used for the majority of the PhD. The focal lengths of $f_1$, $f_2$, $f_3$, \& $f_4$ are $-20\ mm$, $60\ mm$, $150\ mm$, \& $200\ mm$ respectively. Diagram not drawn to scale.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Position detection methods}
In order to accurately capture the dynamics of a trapped particle, 
a position detection system must be utilised. There are 3 possible
methods of position detection: video-analysis, lateral-effect
position sensing, and quadrant photodiodes. The former being 
ideally suited for multiple traps or situations where precision
is not the top priority. In order to match the force measurements
of back-focal plane interferometry requires the camera's frame
rate to exceed $1\ kHz$ which can be difficult to achieve while 
maintaining a decent resolution \cite{Gibson2008}. In comparison
off the shelf back-focal plane detectors can achieve temporal
resolutions anywhere from $10-100\ kHz$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Fourier Optics and 4f correlators}
A 4f correlator is an example of Fourier optics in practice, understanding
that a focused lens takes a Fourier transform of the light profile. 
Consider a laser with a circular Gaussian profile, if you were to place 
a detector there you would pick up the intensity as a function of its 
position within the beam. If however you focused the light into a single 
point (using a +ve focal lens) you are actually seeing a measurement of 
the phase of your laser with position, in which you would see a diffraction
limited spot ($d = \lambda/2nsin(\theta)$), indicating that the laser is 
collimated. In imaging systems, a series of focal lenses can be used to 
filter out unwanted scattering from an image (or in an inverse case 
differentiate between different images), the placement of each lens is shown below.
For our applications a 4f correlator is utilised to ensure that the motion
of the galvano-mirrors does not move the focal point of the laser, allowing 
for a stable trap even while in motion.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Calibration of Tweezer Setup}
Prior to testing optical rotation the trapping laser was calibrated 
using power spectra analysis

@@

Vaterite samples where made by the first preparing equal amounts of 
$CaCl_2$ and $Na_2CO_3$ at a concentration of $0.33M$, at the same time
a vial of $0.33M\ MgSO_4$ was prepared and set aside for later. First
a small vial was filled with $1.5mL$ of $CaCl_2$ followed by $60\mu L$ 
and $90\mu L$ of $MgSO_4$ and $NaCO_3$ respectively, forming a seed solution. 
Next, a larger vial was filled with $5\ mL$, $1.5\ mL$, and $1\ mL$ of
$CaCL_2$, $MgSO_4$, and $NaCO_3$ respectively followed by the seed solution. 
After 10 minutes of slow but continuous mixing a few drops of Agepon was added
to halt the reaction, the solution was filtered and washed 3 times with 
distilled water before being suspended in water. When trapped in circularly 
polarised light, the anisotropic scattering of the sphere results in a periodic 
signal on the QPD. Therefore, the resulting power spectrum is not a Lorentzian
but now also displays peaks that appear at integer multiples of the particles
rotational frequency. 
\begin{figure}[h!]
	\label{fig:vaterite}
	\centering
	\begin{subfigure}{0.4\linewidth}
		\includegraphics[width=\linewidth]{vaterite_sample.jpg}
		\subcaption{}
	\end{subfigure}
	\begin{subfigure}{0.55\linewidth}
		\includegraphics[width=\linewidth]{rotating_psd.png}
		\subcaption{}
	\end{subfigure}
	\caption{(a)Sample vaterite sphere suspended in water and trapped by circular polarised trap. (b) Collected power spectrum from rotating vaterite, peaks in the power spectrum appear at integer multiples of the rotational frequency ($f_{rot} \approx 49.8$ Hz)}
\end{figure}

Liquid crystals are an intriguing example of materials with mixed phase
properties, unlike typical solutes such as Glycine, a liquid crystal
can still maintain some degree of order between its individual molecules
while in the liquid state. This is due to the fact that liquid crystals
are constructed of long ordered molecules that demonstrate a long range
ordering. There are three main types of liquid crystal transition methods:
thermotropic crystals will transition to their liquid crystal phase when 
sufficiently heated; Lyotropic materials can undergo this transition due 
to changes in temperature and concentration; and lastly Metallotropic 
materials - which are composed of both organic and inorganic molecules - 
change phase according to the ratio of organic to inorganic molecules present.
Liquid crystal rotors are rather simple in their production, 
4-Heptyl-4-biphenylcarbonitrile (7CB) was purchased from Sigma Aldrich
and a small amount was added to a vial of distilled water. The solution 
was then heated in a water bath to $25^\circ$ in order to transition the
solid crystal into its liquid crystal state. The individual droplets 
are inherently birefringent and rotate in a circularly polarised trap. 
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.5\linewidth]{LC_sample.png}
	\caption{Liquid crystal undergoing rotation due to the circularly polarised trap.} 
\end{figure}

@@

First we tested the rotational behaviour of vaterite in distilled water, 
samples of vaterite where diluted down and $200\mu L$ was pipetted onto
the sample stage. Due to Van der Waal's forces some of the microspheres 
were stuck together, fortunately individual sphere's were still present.
Over the course of a few weeks multiple sphere's where trapped 
and their rotation speeds were measured via the QPD. 
\begin{figure}[h!]
	\label{fig:vaterite_shear}
	\begin{subfigure}{0.5\linewidth}
		\includegraphics[width=\linewidth]{vaterite_fluid_flow.png}
		\subcaption{}
	\end{subfigure}
	\begin{subfigure}{0.5\linewidth}
		\includegraphics[width=\linewidth]{vaterite_shear_rate.png}
		\subcaption{}
	\end{subfigure}
	\caption{(a) Fluid flow radiating out from the surface of a rotating vaterite sphere. (b) Shear rates computed using Eq.\ref{eq:birefringent_shear}, optimal shear rate is of $3000 s^{-1}$ is indicated by the dotted line. Vaterite radii and rotation frequencies are shown, the laser power was kept constant at 450 mW. Reported rotation rates, and their corresponding fluid flow and shear rates, for vaterite are also plotted alongside lab results.}
\end{figure}

@@

@@

For a simple circular path one can estimate the sphere's speed by the 
radius of its path and the frequency of its orbit $U = R\omega$; however 
for a more complex path, such as an elliptical orbit the curve needs 
to be parametrised. One can describe the position parameter of an ellipse 
as such:

\begin{align}
	r(u) = \left[acos(2\pi u),bsin(2\pi u), 0 \right]
\end{align}

where a and b are the different characteristic radii of an ellipse, if 
we say that $u$ describes time from some initial point we can say $u=t\omega$ 
where omega is the frequency of orbit. Substituting this in and then taking 
the partial derivative of position gives:

\begin{align}
	v(t) = \frac{dr(t)}{dt} = \left[-2\pi a\omega \ sin(2\pi t\omega),\ 2\pi b\omega \ cos(2\pi t\omega),0 \right]
\end{align}

@@

\begin{align}
	u_r(r)=-v(t)cos(\theta)\left(1-\frac{3R}{2r}+\frac{R^3}{2r^3}\right)
\end{align}

@@

\begin{align}
	\dot{\gamma}(r) = \left| \frac{\delta u_r(r)}{\delta r}\right| = v(t)cos(\theta)\left(\frac{3R}{r^2} -\frac{2R^3}{r^4} \right)
\end{align}

Silica beads ($r=1,57 \mu m$) were trapped and moved along an elliptical path

@@

Consider below in Fig.~\ref{fig:stationary_beam} the frames taken from a nucleation 
event in supersaturated glycine solution (S=1.03), the beam is a stationary being 
$\approx3.5 \mu m$ from the droplet edge. After a period of roughly 5 minutes a 
nucleus forms at the trap focus, growing quickly until after roughly $6$ seconds 
the crystal escapes the trap. The key take away to remember is that the beam has no 
real influence over the crystal front,instead the crystal grows outward from the 
centre of the focus.
\begin{figure}[h!]
	\label{fig:stationary_beam}
	\centering
	\includegraphics[width=0.7\linewidth]{frames_no_beam_movement.pdf}
	\caption{Laser induced nucleation at the edge of a droplet of supersaturated 
	glycine solution. (b) shows the first instance of a crystal nucleus, growing 
	quickly through (c)-(e) until after $6.665\ s$ the crystal begins to escape the
	trap.}
\end{figure}

Now while trying to induce fluid flow by optically trapping a silica particle and 
using a galvano-mirror to move the particle through the solution, nucleation events
were observed in which the crystal front follows the path of the laser. See below 
in \textcolor{red}{Fig.XX} where we have the laser focus moving in a small elliptical 
pattern,

>>>>

It should be noted that the galvano-mirror requires the use 
of a Keplerian beam expansion arrangement which reduces
the transmitted laser power due to localised heating of the air.
Afterwards the laser is passed through a dichroic mirror that 
separates incoming infrared and visible light, this is to 
prevent the laser from damaging the CCD camera used for imaging
the trapping plane. The laser is then focused to a diffraction
limited spot by a 1.25 NA objective. By increasing the numerical
aperture of the objective, the gradient force at the focal point 
is increased; the trade-off being that the for higher NA values 
the trapping depth is reduced due to spherical aberrations.
While it is possible to increase the trapping depth \cite{Reihani2006} 
by adjusting the objective's tube length this approach is incompatible 
with our trapping arrangement. A 0.25 NA condenser objective refocuses
the scattered laser light and also provide an aperture for an 
imaging LED to illuminate the focal plane. Samples are loaded 
onto a piezo driven table to that is inserted between the trapping
and condensing objectives; the piezo drivers allow for sub-micron
control of the sample position to a degree as small as a 10 nm. 
To detect and monitor the position of a trapped particle a 
quadrant photo diode (QPD) was utilised. 
\begin{figure}[h!]
	\centering
	\includegraphics[height=\linewidth, angle=270]{tweezer_setup.pdf}
	\caption{Optical tweezer set up used for the majority of the PhD. The focal lengths of $f_1$, $f_2$, $f_3$, \& $f_4$ are $-20\ mm$, $60\ mm$, $150\ mm$, \& $200\ mm$ respectively. Diagram not drawn to scale.}
	\label{fig:setup}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Position detection methods}
In order to accurately capture the dynamics of a trapped particle, 
a position detection system is utilised. There are 3 possible
methods of position detection: video-analysis, lateral-effect
position sensing, and photodiodes. The former being 
ideally suited for multiple traps or situations where precision
is not the top priority. In order to match the force measurements
of back-focal plane interferometry requires the camera's frame
rate to exceed $1\ kHz$ which can be difficult to achieve while 
maintaining a decent resolution \cite{Gibson2008}. In comparison
off the shelf back-focal plane detectors can achieve temporal
resolutions anywhere from $10-100\ kHz$ \cite{BergSoerensen2004}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Fourier Optics and 4f correlators}
A 4f correlator is an example of Fourier optics in practice, understanding
that a focused lens takes a Fourier transform of the light profile. 
Consider a laser with a circular Gaussian profile, if you were to place 
a detector there you would pick up the intensity as a function of its 
position within the beam. If however you focused the light into a single 
point (using a +ve focal lens) you are actually seeing a measurement of 
the phase of your laser with position, in which you would see a diffraction
limited spot ($d = \lambda/2nsin(\theta)$), indicating that the laser is 
collimated. In imaging systems, a series of focal lenses can be used to 
filter out unwanted scattering from an image (or in an inverse case 
differentiate between different images), the placement of each lens is shown below.
\begin{figure}[h!]
	\centering
	\begin{subfigure}{0.475\linewidth}
		\includegraphics[width=\linewidth]{signal_generator.jpg}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{0.475\linewidth}
		\includegraphics[width=\linewidth, height=0.7\linewidth]
		{galvano_mirror_controllers.jpg}
		\caption{}
	\end{subfigure}

	\caption{Signal generator galvano mirror controller, channel 1 controls the x-axis 
		mirror, while channel 2 controls the y-axis mirror. Both channels can be manipulated
		independently.}
\end{figure}

For our applications a 4f correlator is utilised to ensure that the motion
of the galvano-mirrors does not move the focal point of the laser, allowing 
for a stable trap even while in motion. As shown in Fig.~\ref{fig:setup}, after
the galvano-mirror we have our two lenses - $f_3$ and $f_4$ - the former being 
installed $150\ mm$ from the second mirror of the galvano, and the latter being 
installed $200\ mm$ from the back focal plane of the trapping objective. The 
signal generator used was supplied by 'MCS Test Equipment Ltd', allowing for 
dual channel signal control. This allowed us to precisely control the alignment,
amplitude, phase, and frequency of both mirrors making alignment much easier. For
basic trapping calibration the galvano-mirrors were set to a simple DC output, 
providing a fixed spot which operates like a typical optical trap.

@@

Vaterite samples where made by the first preparing equal amounts of 
$CaCl_2$ and $Na_2CO_3$ at a concentration of $0.33M$, at the same time
a vial of $0.33M\ MgSO_4$ was prepared and set aside for later. First
a small vial was filled with $1.5mL$ of $CaCl_2$ followed by $60\mu L$ 
and $90\mu L$ of $MgSO_4$ and $NaCO_3$ respectively, forming a seed solution. 
Next, a larger vial was filled with $5\ mL$, $1.5\ mL$, and $1\ mL$ of
$CaCL_2$, $MgSO_4$, and $NaCO_3$ respectively followed by the seed solution. 
After 10 minutes of slow but continuous mixing a few drops of Agepon was added
to halt the reaction, the solution was filtered and washed 3 times with 
distilled water before being suspended in water. When trapped in circularly 
polarised light, the anisotropic scattering of the sphere results in a periodic 
signal on the QPD. Therefore, the resulting power spectrum is not a Lorentzian
but now also displays peaks that appear at integer multiples of the particles
rotational frequency. 
\begin{figure}[h!]
	\centering
	\begin{subfigure}{0.4\linewidth}
		\includegraphics[width=\linewidth]{vaterite_sample.jpg}
		\subcaption{}
	\end{subfigure}
	\begin{subfigure}{0.55\linewidth}
		\includegraphics[width=\linewidth]{rotating_psd.png}
		\subcaption{}
	\end{subfigure}
	\caption{(a)Sample vaterite sphere suspended in water and trapped by circular polarised trap. (b) Collected power spectrum from rotating vaterite, peaks in the power spectrum appear at integer multiples of the rotational frequency ($f_{rot} \approx 49.8$ Hz)}
	\label{fig:vaterite}
\end{figure}

As shown by Fig.~\ref{fig:vaterite}(b) the power spectra produced still 
demonstrates a Lorentzian curve but modified with these periodic peaks, 
while the Lorentzian can be loosely fitted to the end tail there exists 
no current model for describing the power spectra. The closest approximation
to this was conducted by \cite{Yogesha2012} where they describe the 
rotational motion of ellipsoidal polystyrene particles. The critical assumption
being that the particle perfectly rotates in the $x-y$ plane; however it
has long been suspected that birefringent microspheres experience random
rotations outside of the $x-y$ plane \cite{Bang2020} making it very difficult 
to characterise the forces on rotating microspheres without a proper understanding 
of the optical torque being applied to it.

\subsection{Liquid Crystal Rotors}
Liquid crystals are an intriguing example of materials with mixed phase
properties, unlike typical solutes such as Glycine, a liquid crystal
can still maintain some degree of order between its individual molecules
while in the liquid state. This is due to the fact that liquid crystals
are constructed of long ordered molecules that demonstrate a long range
ordering. There are three main types of liquid crystal transition methods:
thermotropic crystals will transition to their liquid crystal phase when 
sufficiently heated; Lyotropic materials can undergo this transition due 
to changes in temperature and concentration; and lastly Metallotropic 
materials - which are composed of both organic and inorganic molecules - 
change phase according to the ratio of organic to inorganic molecules present.
Liquid crystal rotors are rather simple in their production, 
4-Heptyl-4-biphenylcarbonitrile (7CB) was purchased from Sigma Aldrich
and a small amount was added to a vial of distilled water. The solution 
was then heated in a water bath to $25^\circ$ in order to transition the
solid crystal into its liquid crystal state. The individual droplets 
are inherently birefringent and rotate in a circularly polarised trap. 
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.5\linewidth]{LC_sample.png}
	\caption{Liquid crystal undergoing rotation due to the circularly polarised trap.} 
\end{figure}

@@

First we tested the rotational behaviour of vaterite in distilled water, 
samples of vaterite where diluted down and $200\mu L$ was pipetted onto
the sample stage. Due to Van der Waal's forces some of the microspheres 
were stuck together, fortunately individual sphere's were still present.
Over the course of a few weeks multiple sphere's where trapped 
and their rotation speeds were measured via the QPD. 
\begin{figure}[h!]
	\begin{subfigure}{0.5\linewidth}
		\includegraphics[width=\linewidth]{vaterite_fluid_flow.png}
		\subcaption{}
	\end{subfigure}
	\begin{subfigure}{0.5\linewidth}
		\includegraphics[width=\linewidth]{vaterite_shear_rate.png}
		\subcaption{}
	\end{subfigure}
	\caption{(a) Fluid flow radiating out from the surface of a rotating vaterite sphere. (b) Shear rates computed using Eq.\ref{eq:birefringent_shear}, optimal shear rate is of $3000 s^{-1}$ is indicated by the dotted line. Vaterite radii and rotation frequencies are shown, the laser power was kept constant at 450 mW. Reported rotation rates, and their corresponding fluid flow and shear rates, for vaterite are also plotted alongside lab results.}
	\label{fig:vaterite_shear}
\end{figure}

@@

It is not impossible that fluid shearing could be used in the future to localise
nucleation; but from these results, using individual micro-rotors do not seem like 
an appropriate method. If multiple micro-rotors could be trapped in close proximity 
to one another they could create a large region of fluid where nucleation is more 
likely than the bulk fluid. Micro-rotors have been created that allow for precise
control of suspended micro-particles \cite{Butaite2019} and could potentially be
used to generate sufficient shearing, however these could not be used in this PhD 
as we lacked the necessary hardware to form multiple gradient traps.

@@

For a simple circular path one can estimate the sphere's speed by the 
radius of its path and the frequency of its orbit $U = R\omega$; however 
for a more complex path, such as an elliptical orbit the curve needs 
to be parametrised. One can describe the position parameter of a circular 
path as such:

\begin{align}
	r(u) = \left[rcos(2\pi u), rsin(2\pi u), 0 \right]
\end{align}

If we say that $u$ describes time from some initial point we can say $u=t\omega$ 
where omega is the frequency of orbit. Substituting this in and then taking 
the partial derivative of position gives:

\begin{align}
	v(t) = \frac{dr(t)}{dt} = \left[-2\pi r\omega \ sin(2\pi t\omega),
	\ 2\pi r\omega \ cos(2\pi t\omega), 0 \right]
\end{align}

@@

\begin{align}
	u_r(r)=-|v(t)|^2cos(\theta)\left(1-\frac{3R}{2r}+\frac{R^3}{2r^3}\right)
\end{align}

@@

\begin{align}
	\dot{\gamma}(r) = \left| \frac{\delta u_r(r)}{\delta r}\right| = |v(t)|^2cos(\theta)\left(\frac{3R}{r^2} -\frac{2R^3}{r^4} \right)
\end{align}

Moving a silica bead along an circular path can generate significant fluid 
flow around a larger volume compared to comparable microspheres.

@@

Consider below in Fig.~\ref{fig:stationary_beam} the frames taken from a nucleation 
event in supersaturated glycine solution ($S=1.03$), the beam is a stationary being 
$\approx3.5 \mu m$ from the droplet edge. After a period of roughly 5 minutes a 
nucleus forms at the trap focus, growing quickly (growth rate was approximated using
imageJ to be on the order of $700\ \mu m^2/min$) from the focal point of the trap 
until after roughly $6$ seconds the crystal escapes. Comparing to previous literature
using optical tweezers shows that the growth rate is only loosely connected to the 
solutions supersaturation, local conditions play a much larger role in the growth 
rate than just the concentration \cite{Flannigan2023}. A likely reason that the trap 
is escaped is due to the fact that crystal is far too large to be held in place and 
is in fact still growing as the solution is supersaturated. The key take away to 
remember is that the beam has no real influence over the crystal shape, instead 
it grows outward from the trap focus.
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.7\linewidth]{frames_no_beam_movement.pdf}
	\caption{Laser induced nucleation at the edge of a droplet of supersaturated 
	glycine solution. (b) shows the first instance of a crystal nucleus, growing 
	quickly through (c)-(e) until after $6.665\ s$ the crystal begins to escape the trap.}
	\label{fig:stationary_beam}
\end{figure}

Now while trying to induce fluid flow by optically trapping a silica particle and 
using a galvano-mirror to move the particle through the solution, nucleation events
were observed in which crystal growth follows the laser focus. Shown below in Fig.~\ref{fig:eliptical_beam_1} where we have the laser focus moving in a small elliptical 
pattern; interestingly, due to the addition of the silica suspension we see the presence
of small spheres, these appear too small to be silica beads which have a uniform radius
of $1.57\ \mu m$, we surmise these could be small clusters of Glycine that had previously
been shown to form when the aqueous solutions where irradiated with a focused laser
\cite{Tsuboi2009, Gowayed2021}. While no droplets are seen directly entering the focus a 
nucleus forms close to the droplet edge, unlike in Fig.~\ref{fig:stationary_beam} the 
crystal does not grow out from the focal point evenly; due to the galvano mirror, 
the crystal is simultaneously being moved by and growing around the focal point of 
the trap. Because of this the crystal nucleus lacks a clear morphology at first, 
until roughly $20\ s$ the crystal reaches a almost prismatic structure, with further 
irradiation increasing the size. Interestingly the galvano-mirror allows the trap to 
impart a slight torque on the crystal, as shown in fig.~\ref{fig:eliptical_beam_1}(c) 
and (d), where even though the crystal is not directly in the trap focus it rotates in 
the $x-y$ plane and gets trapped again at a corner. The rotation could not be due to fluid
flow close to the surface of the crystal as trap should have no influence on fluid molecules
smaller than a few hundred nano-meters. In figs.\ref{fig:eliptical_beam_1}(e) and (f), 
the crystal growth is localised to the corner, even though previously the crystal growth 
was roughly uniform (compare figs. \ref{fig:eliptical_beam_1}(b) and (c)). The area growth
rate between figures \ref{fig:eliptical_beam_1}(a) and (d) was approximated using imageJ at
$45.03\ \mu m^2 /min$, where as between figures \ref{fig:eliptical_beam_1}(e) and (f) the 
growth rate at that particular edge was estimated at $42.10\ \mu m^2/min$. 
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.9\linewidth]{frames_eliptical_beam.pdf}
	\caption{Laser induced nucleation at the edge of a droplet of 
		supersaturated glycine solution. (b) shows the first instance 
		of a crystal nucleus, growing quickly through (c)-(e) until 
		after $6.665\ s$ the crystal begins to escape the trap.}
	\label{fig:eliptical_beam_1}
\end{figure}

In this instance $20\ \mu L$ of glycine and water ($S=1.03$) was added to $10\ \mu L$ 
of a dilute water-silica mixture making the solution undersaturated ($S\approx0.7$). 
Nucleation in undersaturated conditions has been reported previously in $D_2O$ 
\cite{Rungsimanon2010} and $H_2O$ \cite{Flannigan2023}. Though notably in both cases the
crystal morphology is not influenced by the location of the laser focus, it has been
shown that polarisation can influence the polymorphic control for simple salts 
\cite{Garetz1996, Garetz2002} but no research has been done into the influence of a 
moving beam front on the growth of a newly formed nucleus.

\section{Influence of a moving beam front on seed crystals}
To see if the above phenomena had any direct influence on a
